---
title: "The Pitch"
author: "Christopher Hughes"
date: "26 December 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The data to visualise

Here's the data that we'll be viewing.

```{R, echo = TRUE}
head(mtcars)

```

## How it can be viewed

A variable can be chosen from the drop-down menu. It will then be plotted as a histogram with the binning number of your choice.

```{r}
    x    <- mtcars[, c("mpg")]  # mtcars data
    bins <- seq(min(x), max(x), length.out = 10 + 1)
    
    # draw the histogram with the specified number of bins
    hist(x, breaks = bins, col = 'darkgray', border = 'white')
```

## It's reactive

Change quickly between your data variable without having to edit your plot.

There aren't many other features or advantages but wait. It's in constant development.

## Where can you access this app from? 

Anywhere in the world. It's on the internet! Anyway, here's a map of where my office is.


```{r}
suppressMessages(library(leaflet))
suppressMessages(library(dplyr))

my_map <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=51.5200, lng=-0.0892, popup = "My Office")
my_map

```